A ``Dream'' Interface Design

### 2014-11-25 dream-design/dream-design.tex
more top-level overview

Many mobile devices use touchscreen keyboards instead of physical keyboards. This allows for a larger display without increasing the size of the device. Furthermore, touchscreen keyboards have the ability to change their layout based on user input and disappear when not needed. To compensate for the lack of tactile feedback provided by physical keys, touchscreen keyboards often include aural feedback in the form of audible clicks from a speaker. Haptic feedback in the form of device vibrations is often included as well.

@@

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that provides a significant amount of tactile feedback. This feedback is designed in a way that can be helpful for individuals with and without visual impairments alike. This design was developed with the usability metrics of learnability, efficiency, and error rate in mind.

My ``dream'' interface design makes use of technology that is currently being created by Tactus, a company in Fremont, California \cite{Tactus}. Tactus brings real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus}). Small fluid channels are routed throughout the Tactile Layer and enable fluid to expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, the prototypes have already received a fair amount of recognition and positive feedback \cite{CNN, I-Zone, PCMag, Wired}. Reviewers articulate how the technology seems to be ``downright magical'' \cite{CNN}. Though the look and feel of Tactus technology is totally futuristic, the technology is supposed to appear in consumer devices early next year \cite{Tactus}. Companies will also be able to customize the panel for different types of buttons, say for example, the buttons on a TV remote. This ``dream'' user interface design makes use of the fact that the possibilities for the panel are varied.

@@

\section{Top-Level Design}
The design of this ``dream'' interface aims to assist users with and without visual impairments alike. The design will use Tactus technology to create a grid-like system for IBSVI so that they can engage their spatial cognition, perception and sensing resources while interacting with touch screens. The design will only enable the grid-like system on-command so to not distract or annoy those who do not benefit from it.

>>>>

Many mobile devices utilize touch screens instead of physical keyboards or buttons. This allows for a larger display without increasing the size of the device. Furthermore, touchscreen keyboards and buttons have the ability to change their layout based on user input and disappear when not needed. To compensate for the lack of tactile feedback provided by physical keys and buttons, touchscreen devices often include aural feedback in the form of audible clicks from a speaker. Haptic feedback in the form of device vibrations is often included as well.

@@

In this investigation, I propose a ``dream'' interface design for touchscreen mobile devices that focuses on providing as much as feedback as possible. This feedback is designed in a way that can be helpful for individuals with and without visual impairments alike. The design in its entirety was created with the usability metrics of learnability, efficiency, and error rate in mind.

My ``dream'' interface design incorporates functionality of a product that is currently being developed by Tactus Technology, a company in Fremont, California \cite{Tactus}. Tactus Technology creates real physical buttons that dynamically appear and disappear into a flat touch screen (see Figure~\ref{tactus}). Small fluid channels are routed throughout the Tactile Layer and enable fluid to expand the top polymer layer to create the physical buttons \cite{Tactus}.

Although this technology from Tactus is extremely bleeding-edge, the prototypes have already received a fair amount of recognition and awards \cite{CNN, I-Zone, PCMag, Wired}. Reviewers have articulated how the technology seems to be ``downright magical'' \cite{CNN}. Though the look and feel of Tatctus technology is totally futuristic, the technology is already beginning to appear in consumer devices. In 2013, Touch Revolution, the ``largest-volume glass projected capacitive multi-touch screen manufacturer in the world'', announced a partnership with Tactus Technology \cite{TactusAvailability}. The technologies are being combined and manufactured into consumer devices today. Companies will also be able to customize the panel for different types of buttons, say for example, the buttons on a TV remote. This ``dream'' user interface design makes use of the fact that the possibilities for the panel are varied.

@@

\section{Top-Level Design}
The design of this ``dream'' interface aims to assist users with visual impairments and users without visual impairments alike. The design includes an optional physical grid, tactile buttons of varying sizes, and auditory feedback.

\subsection{Grid-like Tactile Support}
The design will use Tactus technology to create a physical grid-like layout on the screen. This layout IBSVI so that they can engage their spatial cognition, perception and sensing resources while interacting with touch screens. The design will only enable the grid-like system on-command so to not distract or annoy those who do not benefit from it.
